Using numerical modelling to investigate temperature and wave exposure as drivers

### 2021-03-12 thesis_chapter_2.Rmd
chapter 2 updated, tables to come
tables added. issue with table one header though

```{r include=FALSE}
knitr::opts_chunk$set(cache=FALSE)
knitr::opts_chunk$set(fig.align = "center")
```
# Introduction

@@

@@

>>>>

```{r include=FALSE}
knitr::opts_chunk$set(cache=FALSE)
knitr::opts_chunk$set(fig.align = "center")
```

# Introduction

@@

```{r table 2.1, message= FALSE, warning=FALSE, echo=FALSE}

library(flextable)

morph_table <- read.csv("tables/chapter_2/table_1.csv", sep = ";")
morph_table <- flextable(data = morph_table)
morph_table <- theme_zebra(morph_table, odd_header = "transparent", even_header = "transparent")
morph_table <- set_header_labels(morph_table, Morphological.Characteristic = "Morphological Characteristic", Unit.measurement = "Unit.measurement")
morph_table <- align(x= morph_table, align = "center", part = "all")
morph_table <- set_table_properties(morph_table, width = 1, layout = "autofit")
morph_table

@@

```{r table 2.2, message= FALSE, warning=FALSE, echo=FALSE}

var_table <- read.csv("tables/chapter_2/table_2.csv", sep = ";")
var_table <- flextable(data = var_table)
var_table <- theme_zebra(var_table, odd_header = "transparent", even_header = "transparent")
var_table <- align(x= var_table, align = "center", part = "all")
var_table <- set_table_properties(var_table, width = 1, layout = "autofit")
var_table
```
